---
title: "Spatial averaging"
format: html
editor: visual
author: Josh 
---

## Custom function & loop - spatial averaging

HeatwaveR requires a specific input format to analyse data - a temperature time series dataframe with only two vectors - temperature and date.

Because AODN data is 3 dimensional - a matrix of SST for each recording - we need to average the SST in the given area into one single point average.

This removes the specific features of the area - eddies etc., but allows us to quantify the heat of that part of the EAC over time.

To do this, I wrote a function and a for loop which average each recording's SST matrix into a single mean value, which is then assigned to a new dataframe. This new df is what we can feed into HeatwaveR to obtain our first round of analyses.

The code is still experimental.

```{r}
#The function is called spatav (Spatial Average) and is designed to work with dataframes
spatav_exp2 <- function(df) {
  col_means = sapply(df, mean) #applying mean function to all columns in df
  point_mean = mean(col_means) #applying mean function to all column means
  return(point_mean)
}
```

For loop

```{r}
#time_series is the 3D timeseries to be fed to the loop

#output dataframe (for HeatwaveR)
results <- data.frame()

for (i in seq_along(time_series)) {
  current_result <- spatav_exp2(time_series[[i]]) #spatav used on each df
  results <- rbind(results, current_result) #binding results to new df
}

#Should return usable object :)
```

```{#return point mean}
```
